Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-18 mu/article/article.tex
Changing working station.

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
    as a function of the photon energy and polarization angle $\alpha$ for the
    \emph{up} structure for two energy ranges. The absolute maxima is located
    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared, and the
    local maximum from 1.95\,eV to 2.0\,eV, in the visible, both for
    polarization angles between $25^{\circ}$ and $50^{\circ}$.}
    \label{fig:up-3d-vsz}   
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
    structure. The absolute maximum is located for an energy range from 0.90\,eV
    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
    $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra resulting from
evaluate again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
polarization angle $\alpha$ for the \emph{alt} structure.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related
to the left scale, fixing the energy of the incoming beam to 0.912\,eV for which
value the response is maximized for the \emph{alt} structure. In the same figure
and frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ and in the bottom frame the
corresponding $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ components. Again, the circled and
square boxes indicate the values for which the polarization angle and the
velocity angle are parallel and perpendicular and with arrows are indicated the
corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane. The circled box for the collinear angle corresponds for
angles $\alpha$ and $\gamma_{\mathrm{z}}(\omega,\alpha)$ equal to $53.5^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=12.7$\,Km/s,
and the blue square box indicates the perpendicular angles for values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ with a
value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s. Finally
we found that for variations of $\pm0.5^{\circ}$ of those collinear and
perpendicular angles, presented with the error bars on the boxes, correspond
ranges for the polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and
$95^{\circ} \leq \alpha \leq 175^{\circ}$ covering a wide range of angles
because the response angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ has small
variations for the complete range of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.

@@

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
    energy vs. polarization angle for the \emph{up} structure. The absolute
    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
    range from 0.08\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
    \label{fig:up-vx-comp-rtp-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
    \label{fig:up-vy-comp-rtp-1}

>>>>

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
    as a function of the photon energy and polarization angle $\alpha$ for the
    \emph{up} structure for two energy ranges. The absolute maxima is located
    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared radiation
    range, and two local maxima from 1.90\,eV to 1.93\,eV and  1.96\,eV to
    2.0\,eV, in the visible, all for polarization angles between $25^{\circ}$
    and $50^{\circ}$.}
    \label{fig:up-3d-vsz}   
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
    as a function of the photon energy and polarization angle $\alpha$  for the
    \emph{alt} structure. A local maximum and the absolute maximum are located
    for the energy ranges from 0.67\,eV to 0.73\,eV and 0.90\,eV to 0.93\,eV and
    both for polarization angles between $120^{\circ}$ and $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra resulting from
evaluate again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
energy and polarization angle $\alpha$ of the incoming beam for the \emph{alt}
structure.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related
to the left scale, fixing the energy of the incoming beam to 0.912\,eV for which
value the response is maximized for the \emph{alt} structure. In the same figure
and frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ and in the bottom frame the
corresponding $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ components. Again, the circled and
square boxes indicate the values for which the polarization angle and the
velocity angle are parallel and perpendicular and with arrows are indicated the
corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane. The circled box for the collinear angle corresponds for
angles $\alpha$ and $\gamma_{\mathrm{z}}(\omega,\alpha)$ equal to $53.5^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=12.7$\,Km/s,
and the blue square box indicates the perpendicular angles for values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ with a
value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s. Finally
we found that for variations of $\pm0.5^{\circ}$ of those collinear and
perpendicular angles, presented with the error bars on the boxes, correspond
ranges for the polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and
$95^{\circ} \leq \alpha \leq 175^{\circ}$ covering a wide range of angles
because the response angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ has small
variations for the complete range of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.

@@

    \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
    photon energy and polarization angle $alpha$ for the \emph{up} structure.
    The absolute maxima of both are localized in the energy range from 0.08\,eV
    to 0.10\,eV, in the Far  Infrared, and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
    \label{fig:up-vx-comp-rtp-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
    \label{fig:up-vy-comp-rtp-1}
